Capstone Movielens Report

### 2025-12-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section review: UME Model Regularization.

Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
``` {r  main-script@l}
cv.UME.preset.result$tuned.result |>
  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
```{r, eval=FALSE}
endpoints <- 
  get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)

@@

And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
```{r, eval=FALSE}
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"

@@

Let's visualize the fine-tuning results:
```{r}
UME.rglr.fine_tune.results$tuned.result |>
  data.plot(title = "UME Model Regularization: Fine-tuned result",
              xname = "parameter.value",
              yname = "RMSE",
              xlabel = TeX(r'[$\lambda$]'),
              ylabel = str_glue("Deviation from the best RMSE value (",
                                as.character(round(UME.rglr.fine_tune.RMSE.best, digits = 7)), 
                                ")"),
              normalize = TRUE)
```

@@

#### UME Model Regularization: *Retraining the Model with the best* $\lambda$
\

@@

The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L664) performs this operation:
```{r, eval=FALSE}
best_result <- UME.rglr.fine_tune.results$best_result
UME.rglr.best_lambda <- best_result["param.best_value"]

@@

Finally, we calculate the *RMSE* for the ultimately *Regularized UME Model* and add the definitive result to our _Result Table_:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE for the UME Model after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```

::: {.noteblock data-latex=""}
In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
:::

>>>>

Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
``` {r  main-script@l596}
cv.UME.preset.result$tuned.result |>
  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
```{r  main-script@l608, eval=FALSE}
endpoints <- 
  get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)

@@

And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
```{r  main-script@l617, eval=FALSE}
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L636) provides a visual representation of the *fine-tuning results* we have just computed:
```{r  main-script@l636}
UME.rglr.fine_tune.results$tuned.result |>
  data.plot(title = "UME Model Regularization: Fine-tuned result",
              xname = "parameter.value",
              yname = "RMSE",
              xlabel = TeX(r'[$\lambda$]'),
              ylabel = str_glue("Deviation from the best RMSE value (",
                                as.character(round(UME.rglr.fine_tune.RMSE.best, digits = 7)), 
                                ")"),
              normalize = TRUE)
```

@@

#### UME Model Regularization: *Re-training on the `edx` with the best* $\lambda$
\

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L664) performs this operation:
```{r  main-script@l664, eval=FALSE}
best_result <- UME.rglr.fine_tune.results$best_result
UME.rglr.best_lambda <- best_result["param.best_value"]

@@

Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UME Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L712): 
```{r  main-script@l712, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE for the UME Model after being regularized: %1",
         UME.rglr.retrain.RMSE)
```

Finally, we add the definitive *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L720):
```{r  main-script@l720, eval=FALSE}
RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```
